---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ProjectTemplate

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/avalcarcel9/ProjectTemplate?branch=master&svg=true)](https://ci.appveyor.com/project/avalcarcel9/ProjectTemplate)
[![Travis build status](https://travis-ci.org/avalcarcel9/ProjectTemplate.svg?branch=master)](https://travis-ci.org/avalcarcel9/ProjectTemplate)
[![Codecov test coverage](https://codecov.io/gh/avalcarcel9/ProjectTemplate/branch/master/graph/badge.svg)](https://codecov.io/gh/avalcarcel9/ProjectTemplate?branch=master)
<!-- badges: end -->

The goal of ProjectTemplate is to create a template for project workflows in the PennSIVE working group.

# TODO

- put Data in .Rbuildignore so eventually figure out where to best put a folder we are saving to
- put tests in .Rbuildignore since they are empty. Eventually add tests
- put results_generation.R in git ignore for now put it back later

## Installation

You can install the released version of ProjectTemplate from [GitHub](https://github.com/avalcarcel9/ProjectTemplate) with:

```{r, eval = FALSE}
remotes::install_github("avalcarcel9/ProjectTemplate")
```

## Example

First generate the data:

```{r, eval = FALSE, echo = TRUE}
set.seed(23)
# Run the function
data_generation(iter = 10000,
                n = 1000,
                mu_x = 23,
                sd_x = 10,
                mu_y = 9,
                sd_y = 15,
                cores = 1)
```

Then run code that compiles the project results:
- This may be done on the cluster and then results are pulled down locally
