---
title: "ProjectTemplate_Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ProjectTemplate_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ProjectTemplate)
```


# Rmd First Method

This template and workflow is inspired by

1. [https://rtask.thinkr.fr/blog/rmd-first-when-development-starts-with-documentation/](https://rtask.thinkr.fr/blog/rmd-first-when-development-starts-with-documentation/)

# Workflow

Steps:

1. Readme

- Exploration of a baby project
- Code and annotation of code/data
- Order to run things

2. Project/Package Setup

- Set up and R package with a project once the project starts coming to life
- Convert some of the exploratory Readme code to R functions
- Document what data you're using and where it is
- Create R functions
  - Data generation function
  - Results function
  - Paper
  - Supplemental code called by the data generation or results function
  
3. Set up a vignette to organize your thoughts and discuss the order of the code

